Compare pseqs

### 2019-05-17 comparepseqs.Rmd
Less memory

alphadiversity <-  mclapply(dset, function(x)
    list(min =  calculateglm(x, modelstring = fo.alpha.min),
         full = calculateglm(x, modelstring = fo.alpha.full)),
    mc.cores = length(pseq))
```

```{r dissimilarity matrix}
if (!file.exists("rds-comparepseqs/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = length(pseq))
    saveRDS(bray.dist.matrix, file = "rds-comparepseqs/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds-comparepseqs/comparepseqs_bray_matrix.rds")
}
```

@@

    betadiversity <- mclapply(c2l(names(pseq)), function(x)
        list(min = calculateadonis(dset = meta(pseq[[x]]),
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1000),
             full = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1000)),
        mc.cores = length(pseq))

     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

>>>>

alphadiversity <-  mclapply(dset, function(x)
    list(min =  calculateglm(x, modelstring = fo.alpha.min),
         full = calculateglm(x, modelstring = fo.alpha.full)),
    mc.cores = length(dset))
```

```{r dissimilarity matrix}
if (!file.exists("rds-comparepseqs/comparepseqs_bray_matrix.rds")) {
    bray.dist.matrix <- mclapply(pseq, function(x) calculate.beta.matrix(x), mc.cores = length(pseq))
    saveRDS(bray.dist.matrix, file = "rds-comparepseqs/comparepseqs_bray_matrix.rds")
} else {
    bray.dist.matrix  <- readRDS("rds-comparepseqs/comparepseqs_bray_matrix.rds")
}
rm(pseq)
```

@@

    betadiversity <- mclapply(c2l(names(dset)), function(x)
        list(min = calculateadonis(dset = dset[[x]],
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1000),
             full = calculateadonis(dset = dset[[x]],
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1000)),
        mc.cores = length(dset))

     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
        betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
    }
rm(bray.dist.matrix)
```
